Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-25 ms.tex
time series test for multiple apertures on the same array

>>>>

\begin{figure*}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n487Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{}}}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{Apertures}}}
{\gridline{\fig{individual_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.49\textwidth}{Time Series of Apertures}}}
\caption{Time series for 2 apertures on each detector.}\label{fig:twoApPerDetector}
\end{figure*}
